\documentclass{beamer}
\title % (optional, only for long titles)
{Marking Work}
%\subtitle{Evidence from India}
\author[Author, Anders] % (optional, for multiple authors)
{Andrei~Purice \and Alexandru~Tache}

\subject{Marking Supervisions}
\usetheme{Singapore}
\begin{document}
	\frame{\titlepage}
	\begin{frame}
    	\frametitle{Current Problems}
 
   	   	\begin{itemize}
   	   		\item Work will eventually get lost
   	   		\item Supervisors have to manage and print tens of emails.
   	   		\item There is no easy way for a DoS to look at a students work.
  	   	 \end{itemize}	   	 
  	\end{frame}
  	
  	\begin{frame}
    	\frametitle{A bin for every supervision}
    	\begin{itemize}
    		\item All the work for the supervision is organized in a single place
    	    \item We can generate PDFs in different formats with all the work of the students  
    		\item Work is kept for all eternity. 
    		\item Work can be accessed by DoSes, or anyone else with appropriate permission.
    	\end{itemize}
    \end{frame}
    \begin{frame}
    	\frametitle{What it means for the student}
    	\begin{itemize}
    		\item Work will be submitted as either PDF, TxT or as scanned images.
    		\item Students will have to select the questions on their work. This can be done:
    		\begin{itemize}
    			\item Automatically using some special markup for the ones that are computer readable (PDF, TxT)
    			\item Manually using a web interface we provide.    			\end{itemize}
    	\end{itemize}    	
    \end{frame}
    
    \begin{frame}
    	\frametitle{Back to marking work}
    	\begin{itemize}
    		\item We provide PDFs in different formats (by student, by question, etc)
    		\item Those PDFs can be annotated using Xournal (or other tools)
    		\item Once reuploaded we detect and store the annotations made on the pdf.
    	\end{itemize}
    \end{frame}
    
    \begin{frame}
    	\frametitle{New ways to improve the supervision}
    	\begin{itemize}
    		\item Peer marking. Students can mark each others work in a bin.
    		\item Students can review their marked work before the supervision.
 
    	\end{itemize}
    \end{frame}
    \begin{frame}
    	\frametitle{The end}
    \end{frame}
\end{document}